\chapter{Conclusion}
Even though not all the tasks of the assignment were possible to accomplish with the method chosen, we think that the project was a huge success. The main goals of a professionally built, easy to use, directive and steerable loudspeaker were reached. The ultrasound measurements, in Section \ref{6_sec:ultrasonic}, and the human expertise tests, in Section \ref{6_sec:expertise_test}, objectively showed this. Additionally, we think we brought new ideas into how parametric loudspeaker arrays are built by utilising signal processing methods such as the sigma delta modulation.     
\section{Continuing Work}
Although the final product provide a rich set of features, there are some aspects to improve or features to add. Of particular note is the fact that the system is designed for future enhancements. As an example, the flash storage of the Raspberry Pi Compute Module 4 provides lots of additional storage for larger software editions. The following continuations are possible:

\bigskip
\begin{itemize}
		\item Beam-Focusing improvement
		\item Higher order sigma-delta-modulator
		\item Improve wireless performance with external antenna
		\item Develop Remote or app to control the Audio-Beamformer
		\item Frequency Response Measurement and compensation 
\end{itemize}
\newpage

\section{Personal Reflections}
\subsubsection{Florian Baumgartner}
This bachelor's thesis proved to by very challenging, since it covered pretty much every field of electrical engineering. This, however, made it very attractive to work on the project, due to the enormous amount of variety in different topics. I personally could make use of my previously gained knowledge to accelerate the development process. It was a fantastic experience to design a fully working and professional looking product in such a small time frame. I'm very happy with the end result and hope that it will satisfy its purpose of convincing potential new students to start studying electrical engineering. It was a pleasure to work with Thierry Schwaller and we had overall a great time working on this project.

\subsubsection{Thierry Schwaller}
I am personally really proud of the things we've reached throughout this bachelor's thesis. I am convinced that the Audio-Beamformer could become a commercial product if more research is done. 
Additionally, I learned a lot during this assignment about the theory behind the inner workings of phased arrays and the difficulties in connecting theory to the real world. 
The collaboration with Florian Baumgartner helped me a lot to see and try new angles to solve a problem. 